---
title: "Great Learnings: Financial Analyst"
subtitle: "Assignment"
author: 
  name: "Anurima Dey"
date: 21st-October-2020
output: html_notebook
---

# Problem statements: 

**1. Perform Univariate analysis on the data 'Latest'**
**2. Perform Bivariate analysis on data 'Latest' with Prospect Stage = Enrolled as point of interest. Business wants to understand what factors drive erollments?**
**3. Data 'Trails' gives the history of all the sales activities done to nurture a lead. Could you identify the variables that infuence conversion of a lead into enrollment?**


```{r}
latest.file <- readxl::read_xlsx("latest - orig.xlsx")
trail.file <- readxl::read_xlsx("trails - orig.xlsx")
```

```{r}
head(latest.file)
```
```{r}
head(trail.file)
```
```{r}
colnames(latest.file)
```
```{r}
str(latest.file)
```

```{r}
summary(latest.file)
```

```{r}
plot(latest.file[,c("Score", "EngagementScore","mx_Exp_In_Years" )])
```


Make a proper function to obtain the min, max, avg, %null, and all the quantiles, and keep adding the columns in a data frame using rbind

```{r}
# the quantitative variable 
score <-  latest.file$Score

# minimum score 
min <- min(score, na.rm = TRUE)

# maximum score
max <- max(score, na.rm = TRUE)

# average score
avg <- mean(score, na.rm = T)

# % null values
null <- sum(is.na(score))/length(score)*100
```

```{r}
quantitative_vars <- cbind(as.data.frame(min), as.data.frame(max), as.data.frame(avg), as.data.frame(null), t(data.frame(quantile(score, c(seq(0.05, 0.95, 0.05)), na.rm = TRUE))))

```

```{r}
quantitative_vars
```

```{r}
# the quantitative variable 
Engagementscore <-  latest.file$EngagementScore

# minimum score 
min <- min(Engagementscore, na.rm = TRUE)

# maximum score
max <- max(Engagementscore, na.rm = TRUE)

# average score
avg <- mean(Engagementscore, na.rm = T)

# % null values
null <- sum(is.na(Engagementscore))/length(Engagementscore)*100
```

```{r}
Engagementscore <- cbind(as.data.frame(min), as.data.frame(max), as.data.frame(avg), as.data.frame(null), t(data.frame(quantile(Engagementscore, c(seq(0.05, 0.95, 0.05)), na.rm = TRUE))))
```

```{r}
quantitative_vars <- rbind(quantitative_vars, Engagementscore)
```

```{r}
row.names(quantitative_vars) <- c("Score", "Engagementscore")
```

# The first table is accomplished

```{r}
quantitative_vars
```

# table two: for qualitative variables

```{r}
as.factor(latest$mx_Preferred_Campus)
```























# Working on Latest file

Find the missing percentage of each column

```{r}
missing_percentage <- colSums(is.na(latest.file))/dim(latest.file)[1] * 100
```

```{r}
missing_percentage
```
We shall ideally discard variables with more than 30% missing values

The variables with more than 30% missing values are:
```{r}
colnames(latest.file)[missing_percentage >=30]
```

Variables that remains

```{r}
latest <- subset(latest.file, select = -c(mx_Country, mx_Mode_of_Instruction, mx_Application_Date, 
                                           mx_Industry, mx_UG_Degree, mx_UG_Passing_Year, mx_PG_Degree,
                                           mx_PG_Passing_Year, mx_Batch_Code, mx_City, mx_Device_details))

head(latest)
```
The columns thata are presesnt now in latest

```{r}
colnames(latest)
```

Finding the unique values in each columns
And pointing out their mistakes

mx_prefered_campus: mistakes = "Select One", NA, "BABI....."

```{r}
unique(latest$mx_Preferred_Campus)
```
mx_exp_in_years: "42339", NA, "Select One"
 
```{r}
unique(latest$mx_Exp_In_Years)
```


```{r}
unique(latest$DoNotCall)
```
```{r}
unique(latest$DoNotEmail)
```
```{r}
unique(latest$Source)
```

SourceMedium: NA, factoring doesnot matter
Sourcecampaign: NA, factoring doesnot help


Prospect stage:

__This variable is important__: "Enrolled" 

__This is our dependant variable__
The state of this is dependent on the other variables.

```{r}
unique(latest$ProspectStage)
```

__Score, Engagement score__ are two Quantitative variables

```{r}
unique(latest$Score)
```
Na there

```{r}
table(latest$mx_Current_Interested_Program)
```


```{r}
table(latest$ProspectStage)
```

```{r}
barplot(latest$Score)
```








